Outdated and License-Violating Code on Stack Overflow

### 2017-10-09 cloverflow-tse/cloverflow.tex
Latest update on RQ1, 2, and 3.

\subsection{Stack Overflow Developers' Survey} We support our findings of
outdated and license-violating code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and licensing-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our \FIXME{technical
	report/website?} ~\footnote{Survey--Stack Overflow Answerers:
	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.

@@

The statistics on clones obtained from the merged clone data set are
presented in \Cref{tab:snippets}. Simian and SourcererCC
reported clones in 560 snippets, approximately 1\% of the
72,365 Stack Overflow snippets, associated with 59 Qualitas
projects. For the cloned Stack Overflow snippets, the
average ratio of cloned code is 54.22\%.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{p{2.2cm}rrrr}
		\toprule
		Set & Pairs & Snippets & Projects & Cloned ratio \\
		\midrule
		Reported clones & 2,302 & 590 & 63 & 53.10\% \\ 
		\midrule
		TP from manual validation & 2,076 & 560 & 59 & 54.22\% \\ % <-- for avg. cloned ratio, use scripts in ~/Downloads/stackoverflow/scripts/checking
		\bottomrule
	\end{tabular}
\end{table}

During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 1,216 true positive clone pairs between 516 Stack
Overflow snippets and 75 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 3,636 clone pairs, we found 1,216 pairs as true positives which 
	account for 75 Qualitas projects and
	516 Stack Overflow code snippets.}

%\FIXME{Should we have removed the AC clones right at the beginning?}

@@

As shown in \Cref{tab:online_clone_classification_results}, the automatic
classifier helped us to classify 28,897 clone pairs into
pattern \textbf{BP}. Then, we relied on a manual classification
% to qualitatively investigate the patterns of
%online code cloning 
on the remaining 3,636 pairs by following the classification process
in \Cref{fig:classification_process}. 
%To achieve this, we classified all 32,533
%selected clone pairs according to the classification process 
%in \Cref{fig:classification_process}.  
%
%There were 3,636 pairs left for the manual check. 
The classification results are shown in \Cref{tab:classification_good_o} 
and explained in the following.

%\begin{table}
%	\centering
%	\caption{No.~of online clones candidates for the classification}
%	\label{tab:online_clone_classification_results}
%	%\small
%	%	\resizebox{\columnwidth}{!}{%
%	\begin{tabular}{lrrr}
%		\toprule
%		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
%		& & Auto & Manual \\
%		\midrule 
%		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
%		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
%		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
%		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
%		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
%		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
%		\midrule
%		Total  & 32,533 & 28,897 & 3,636 \\ 
%		\bottomrule
%	\end{tabular} %
%	%}
%\end{table}

\begin{table*}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{rrrrrrrr}
		\toprule
		QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		239 (149) & 1 (1) & 208 (119) & 107 (65) & 1,505 (217) & 16 (9) & 226 (53) & 2,302 (560) \\
		\bottomrule
	\end{tabular} 
	%}
\end{table*}

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
online clone pairs with evidences of cloning from 19 Qualitas projects to
Stack Overflow. They include 3, 14, 86, and 9 pairs from the
\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
them have a statement in the Stack Overflow post saying that the code
is ``copied'', ``borrowed'' or ``modified'' from a specific file or class in a
Qualitas project. For example, according to the motivating example in 
\Cref{fig:before-after}, we found evidence in the Stack Overflow 
Post 22315734 saying that \textit{``Actually, you can learn how to compare 
	in Hadoop from WritableComparator. Here is an examle that borrows 
	some ideas from it.''}

The most cloned projects are \textsf{hibernate} and
\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
pairs), and \textsf{hadoop} (12 pairs). The clones are used as
examples and are very similar to their original Qualitas code with
limited modifications.

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
any pairs with evidence of cloning from Stack Overflow to Qualitas
projects. This is very likely due to the age of the Qualitas corpus as
another study~\cite{An2017} showed the presence of clones from Stack
Overflow in newer open source data sets.

\textbf{EX: External Sources.} We found 200 clone pairs with
evidence of cloning from external sources to Stack Overflow and to Qualitas.  
They include 4, 44, 146, and 6 pairs from the \textit{good}, \textit{ok'},
$S_D'$, and $N_D'$ set respectively. All of them contain statements
giving an external source of the cloned code.  For example, Stack
Overflow Post 9549009 contains a code comment saying \textit{``Copied
	shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''}.

@@

These findings complement a study of clones between software
projects~\cite{Svajlenko2014}. We found that cloning can also
happen among different sources on the Internet just like software
projects. There are 30 clone pairs that originated from programming
websites. For example, we found a clone of a snippet to convert
numbers into words which is copied from
\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
Overflow and the \textsf{compiere} project code contain an
attribution to the original source. Another example is a snippet
to generate graphical \textit{Perlin noise}. It is copied from
\url{http://mrl.nyu.edu/~perlin/noise/} and is used on Stack
Overflow and in the \textsf{aoi} project with
attribution.
% The original code of the 15 clone pairs do not have licensing
% information so these clones do not violate any license.
There are other EX pairs which are copied from third-party
libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
project.

\textbf{UD: Unknown Direction.} We found 359 online clone pairs with
no evidence of cloning between Qualitas and Stack Overflow but with a
high code similarity that suggests cloning. 
% They include 15, 20, 293, and 31 pairs from the \textit{good},
% \textit{ok'}, $S_D'$, and $N_D'$ set respectively.
The most cloned projects is \textsf{netbeans} with
93 clone pairs. Most of the clones are a large chunk of code handling
GUI components. Although these GUI clones might be auto-generated by
IDEs, we did not find any evidence. The second most cloned project is
\textsf{jung2} (62 pairs), a network and graph framework, followed by
\textsf{eclipse-SDK} (37 pairs).
% There are several Stack Overflow snippets that are identical to code
% in \textsf{jung2}.

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
clone pairs found in this study. %Although we have removed some of the
%boiler-plate code with filters before the analysis, we still 
We observed 29,330 such clone pairs. The BP clone pairs account for
90\% of all clone pairs we classified. The majority of them are
{\small{\texttt{equals()}}} methods.

\textbf{IN: Inheritance/interface.} There were 112 clone pairs found
to be similar because they implement the same interface or inheriting
from the same class. An example is the two implementations of
{\small{\texttt{MouseListener}}} that share similar
{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
and {\small\texttt{mouseReleased}}.

\textbf{AC: Accidental Clones.} There were 2,420 accidental clone
pairs. Mainly, they are false positive clones caused by code
normalisation. 
% However, the original source code were still different enough when
% we manually classified them.
Other clone instances include {\small\texttt{finally}} or
{\small\texttt{try-catch}} clauses that were accidentally the same due
to their very small sizes, and similar {\small\texttt{switch-case}}
statements.

%For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code. Our regular expressions could automatically classified 16,800 of them into BP. The investigator checked the 1,001 remaining pairs manually. As a result, we found 86 QS, 294 UD, 145 EX, 17,074 BP, 74 IN and 128 AC pairs. For 88 $N_D$ clone pairs, 10 of them were automatically classified into BP and 78 were manually classified. We found 9 QS, 35 UD, 6 EX, 17 BP, 8 IN, and 13 AC respectively.

%FIXME: We probably have to discuss IN clones.
%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
\textbf{To answer RQ2, we found that a large amount of the clone pairs
	between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
	(29,330) or accidental clones (2,420) with no evidence that the code
	has actually been copied. Nevertheless, we found 112 pairs with
	strong evidences to be cloned from 19 Qualitas projects to Stack Overflow and
	200 pairs were found to be cloned to Stack Overflow from external
	sources.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

%In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow. From the manual investigation, we found 523 true positive online clone pairs. With this set of true clones, we investigated further and found that there are two potential issues, outdated code and software licensing violation.

%\subsubsection{Outdated Clones}

We discovered 64 outdated online clone pairs out of 112 pairs. As
shown in \Cref{fig:outdated}, \textsf{spring} has the highest number
of 17 outdated pairs, followed by 7 from \textsf{hibernate} and
\textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
outdated code in % \textsf{hadoop}'s
{\small{\texttt{WritableComparator.java}}} 
from \textsf{hadoop} shown in
\Cref{fig:before-after}, we also found a few outdated code elements
which contained a large amount of modifications. For example, the code
snippet in Stack Overflow post 23520731 is a copy of
{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
has been heavily modified on February 5, 2016.

In the 64 outdated pairs, we found 5 ``dead'' snippets. These snippets
cannot be located in the latest version of the projects. For example,
the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
\textsf{spring}, was deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
Beams on January 20, 2012, two years after it was
posted.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{freshness}
	\caption{Status of the 112 QS online clone pairs}
	\label{fig:outdated}
\end{figure}

>>>>

\subsection{Stack Overflow Developers' Survey} We support our findings of
outdated and license-violating code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and licensing-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our research note~
\FIXME{add URL to the RN}.

@@

The statistics on clones obtained from the merged clone data set are
presented in \Cref{tab:snippets}. Simian and SourcererCC
reported clones in 460 snippets, approximately 0.6\% of the
72,365 Stack Overflow snippets, associated with 59 Qualitas
projects. For the cloned Stack Overflow snippets, the
average ratio of cloned code is 53.10\%.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{p{2.2cm}rrrr}
		\toprule
		Set & Pairs & Snippets & Projects & Cloned ratio \\
		\midrule
		Reported clones & 2,302 & 460 & 59 & 53.10\% \\ 
		\midrule
		TP from manual validation & 2,076 & 449 & 59 & 54.22\% \\ 
		\bottomrule
	\end{tabular}
\end{table}

During the manual investigation of 2,302 clone pairs, we identified 226 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 449 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 54.22\%.

\textbf{To answer RQ1, we found more than half of Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
	account for 59 Qualitas projects and
	449 Stack Overflow code snippets.}

@@

We performed a manual classification
of the 2,302 merged clone pairs by following the classification process
in \Cref{fig:classification_process}. 
The classification results are shown in \Cref{tab:classification_good_o} 
and explained in the following.

\begin{table*}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrrrrr}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		Before consolidation & 248 & 1 & 199 & 107 & 1,505 & 16 & 226 & 2,302 \\
		After consolidation & 154 & 1 & 111 & 65 & 217 & 9 & 53 & 560 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table*}

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
pairs with evidences of cloning from Qualitas projects to Stack Overflow.
However, we observed that, in some cases, a cloned code snippet on Stack
Overflow matched with more than one code snippet in Qualitas projects. This is
because there were also code cloning inside Qualitas projects themselves. To
avoid double counting of such online clones, we consolidated clone pairs having
the same Stack Overflow snippet, starting line, and ending line into a single
clone pair. We finally obtained 154 QS pairs having unique Stack Overflow code
snippets and associated with 23 Qualitas projects listed in
\Cref{tab:qs_qualitas_projects}. The most cloned projects are \textsf{hibernate}
and \textsf{spring} with 24 clone pairs, followed by \textsf{eclipse} (21
pairs), \textsf{jung2} (19 pairs), \textsf{spring} (17 pairs), and
\textsf{jfreechart} (13 pairs). The clones are used as examples and are very
similar to their original Qualitas code with limited modifications. Most of them
have a statement in the Stack Overflow post saying that the code is ``copied'',
``borrowed'' or ``modified'' from a specific file or class in a Qualitas
project. For example, according to the motivating example in
\Cref{fig:before-after}, we found evidence in the Stack Overflow Post 22315734
saying that \textit{``Actually, you can learn how to compare in Hadoop from
	WritableComparator. Here is an examle that borrows some ideas from it.''}

\begin{table}
	\centering
	\caption{Qualitas projects associated with QS and UD online clone pairs}
	\label{tab:qs_qualitas_projects}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrlr}
		\toprule
		\multicolumn{2}{c}{QS} & \multicolumn{2}{c}{UD} \\
		\midrule
		Project & Pairs & Project & Pairs\\
		\midrule
		hibernate & 24 & netbeans & 11 \\
		eclipse & 21 & eclipse & 8 \\
		jung2 & 19 & jstock & 5 \\
		spring & 17 & compiere & 5 \\
		jfreechart & 13 & ireport & 4 \\
		hadoop & 10 & jmeter & 4 \\
		log4j & 8 & jung2 & 3 \\
		tomcat & 8 & jhotdraw & 3 \\
		struts & 5 & c-jdbc & 3 \\
		lucene & 4 & log4j & 3 \\
		weka & 4 & wct & 2 \\
		junit & 3 & hibernate & 2 \\
		poi & 3 & tomcat & 2 \\
		compiere & 2 & spring & 1 \\
		jasperreports & 2 & rssowl & 1 \\
		jboss & 2 & mvnforum & 1 \\
		jgraph & 2 & jfreechart & 1 \\
		jstock & 2 & jboss & 1 \\
		antlr & 1 & hadoop & 1 \\
		itext & 1 & geotools & 1 \\
		jgrapht & 1 & freemind & 1 \\
		ant & 1 & findbugs & 1 \\
		c-jdbc & 1 & cayenne & 1 \\
		\bottomrule
	\end{tabular} 
	%}
\end{table}

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We found one pair with
evidence of cloning from Stack Overflow post ID 698283 to
{\small\texttt{POIUtils.java}} in \textsf{jstock} project. The user
\textsf{yccheok} who asked the question in Stack Overflow is the author of
\textsf{jstock}. The question is about determining the right method to call
among 7 overloading methods of {\small\texttt{setCellValue}} during runtime. We
could not find evidence of copying or attribution to Stack Overflow in
\textsf{jstock}. However, considering that the 25 lines of code of
{\small\texttt{findMethodToInvoke}} method depicted in \Cref{fig:jstock_code} in Stack
Overflow is identical to the code in \textsf{jstock} including comments, it is almost certain that
the two code snippets form a clone pair. In addition, Stack Overflow answer was
posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.

\begin{figure}
	\begin{lstlisting}
private Method findMethodToInvoke(Object test) {
  Method method = parameterTypeMap.get(test.getClass());
  if (method != null) {
    return method;
  }

  // Look for superclasses
  Class<?> x = test.getClass().getSuperclass();
  while (x != null && x != Object.class) {
    method = parameterTypeMap.get(x);
    if (method != null) {
      return method;
    }
    x = x.getSuperclass();
  }

  // Look for interfaces
  for (Class<?> i : test.getClass().getInterfaces()) {
    method = parameterTypeMap.get(i);
    if (method != null) {
      return method;
    }
  }
  return null;
}
	\end{lstlisting}\vspace{-2ex}
	\caption{The {\small\texttt{findMethodToInvoke}} that is found to be copied from Stack Overflow post 698283 to {\small\texttt{POIUtils}} class.}
	\label{fig:jstock_code}
\end{figure}

We did not find other online clones besides the one mentioned above. 
This very low number of SQ clone pair is very likely due to the age of the
Qualitas corpus as another study~\cite{An2017} showed the presence of clones
from Stack Overflow in newer open source data sets. This is expected and
comes from our experimental design since
we are more interested in a cloning direction from Qualitas to Stack Overflow.

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{ex_sources}
	\caption{Original sources of EX clone pairs}
	\label{fig:ex_sources}
\end{figure}

\textbf{EX: External Sources.} We found 199 clone pairs with evidence of cloning
from external sources to Stack Overflow. After getting rid of duplicated SO
snippets due to multiple intra-clone instances in Qualitas, we obtained 111 EX
pairs. Fifty pairs provide evidences of copying to both Stack
Overflow and Qualitas while the rest (61) only provides evidence of copying to
Stack Overflow. All of them contain statements giving an external source of the
cloned code which fall into six groups as displayed in \Cref{fig:ex_sources}. 
We discovered that 63 EX online clone pairs are copied from source code of classes or 
methods in Java SDK, 18 pairs are from websites, 15 pairs are from open source systems,
11 pairs are from Java official documentations from Sun Microsystems or Oracle,
3 pairs are from books, and 1 pair is from a company project.
For example, Stack Overflow Post
9549009 contains a code comment saying \textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

@@

These findings complement a study of clones between software
projects~\cite{Svajlenko2014}. We found that cloning can also happen among
different sources on the Internet just like software projects. The are 18 clone
pairs that originated from programming websites including \url{www.java2s.com}
and \url{exampledepot.com}. Moreover, there is one snippet which comes from a
research website. We found that a snippet to generate graphical \textit{Perlin
	noise} is copied from NYU Media Research Lab
(\url{http://mrl.nyu.edu/~perlin/noise/}) website and is used on Stack Overflow
and in the \textsf{aoi} project with attribution. There are other EX pairs which
are copied from open source libraries or Java SDK such as \textsf{Mozilla
	Rhino}, \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}, and
the \textsf{bouncycastle} cryptography project.

\textbf{UD: Unknown Direction.} We found 107 online clone pairs, reduced to 65
pairs after consolidating the clones, with no evidence of cloning between Qualitas
and Stack Overflow but with a high code similarity that suggests cloning. 
The most cloned projects is \textsf{netbeans} with 11 clone pairs. Most of the
clones are a large chunk of code handling GUI components. Although these GUI
clones might be auto-generated by IDEs, we did not find any evidence. The second
most cloned project is \textsf{eclipse} (8 pairs), followed by \textsf{jstock},
a free stock market software, and \textsf{compiere}, a software and customer
relationship management (CRM) system, (5 pairs).

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
found in this study. We observed 1,505 such clone pairs and 217 after
consolidation. The BP clone pairs account for 65\% of all clone pairs we
classified. The majority of them are {\small{\texttt{equals()}}} methods.

\textbf{IN: Inheritance/interface.} There were 16 clone pairs, 9 pairs after
consolidation, found to be similar because they implement the same interface or
inheriting from the same class. An example is the two implementations of a
custom data type which implements {\small\texttt{UserType}}. They share similar
{\small\texttt{@Override}} methods of {\small\texttt{deepCopy}},
{\small\texttt{isMutable}}, {\small\texttt{assemble}},
{\small\texttt{disassemble}}, and {\small\texttt{replace}}.

\textbf{AC: Accidental Clones.} There were 226 accidental clone
pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
normalisation and false type-3 clones from SourcererCC. 
Examples of the AC clone instances include {\small\texttt{finally}} or
{\small\texttt{try-catch}} clauses that were accidentally the same due
to their very small sizes, and similar {\small\texttt{switch-case}}
statements.

\textbf{To answer RQ2, we found 154 pairs with
	strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
	was cloned from Stack Overflow to Qualitas, and
	111 pairs were found to be cloned to Stack Overflow from external
	sources. However, the largest amount of the clone pairs
	between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
	(217), followed by 65 clone pairs with no evidence that the code has actually been copied,
	and 16 pairs of clones due to implementing the same interface or inheriting the same class.}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.8\linewidth]{outdated}
	\caption{Outdated QS online clone pairs group by projects}
	\label{fig:outdated}
\end{figure*}

We discovered 101 outdated online clone pairs out of 154 pairs. As shown in
\Cref{fig:outdated}, \textsf{hibernate} has the highest number of 19 outdated
pairs, followed by 14 from \textsf{spring}, 13 from \textsf{eclipse}, and 9 from
\textsf{hadoop}. Besides the two examples of outdated code in % \textsf{hadoop}'s
{\small{\texttt{WritableComparator.java}}} and
{\small{\texttt{StringUtils.java}}} from \textsf{hadoop} shown in
\Cref{fig:before-after} and \Cref{fig:before-after_2}, we also found a few
outdated code elements which contained a large amount of modifications. For
example, the code snippet in Stack Overflow post 23520731 is a copy of
{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code has been
heavily modified on February 5, 2016.

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{mod_types}
	\caption{Six code modification found in the latest versions of the outdated clone pairs}
	\label{fig:mod_types}
\end{figure}

We analysed code modifications which made Stack Overflow code outdated by going
though commits and git blame information. The summary of six code modification
types found in the 101 outdated online clone pairs are displayed in
\Cref{fig:mod_types} including statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often
code changes found is statement modification (49 occurrences), followed by statement
addition (29 occurrences), statement removal (18 occurrences), changing of method
signature, i.e.~API change (16 occurrences), and method rewriting (15 occurrences).
Moreover, in the 101 outdated pairs, we found 15 ``dead'' snippets. These snippets
cannot be located in the latest version of the projects. For example,
the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
\textsf{spring}, was deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
Beams on January 20, 2012, two years after it was
posted.

@@
